The Heavy Photon Search Test Detector

### 2014-03-11 hps-testrun-nim.tex
Shifting around parts of the intro, trying to be consistent on HPS Test workding

%% main text
\section{Introduction}
\label{introduction}
Heavy photons, aka "hidden sector" or "dark" photons, or from here on \Aprime{}, are particles with 
mass $10-1000$~MeV 
which couple weakly to the Standard Model photon~\cite{Holdom:1985ag}, so can be radiated by 
electrons, and can decay 
into \ee pairs, albeit at rates far below those of QED trident processes. They have been suggested by 
numerous Beyond Standard Model theories and as an explanation of the current muonic $g-2$ 
anomaly, and may couple directly to hidden sector particles that may constitute all or some of the 
dark matter~\cite{ArkaniHamed:2008qn}. 
Current phenomenology highlights the $20-1000$~MeV/c$^{2}$ mass range, and 
suggests that \Aprime's couple to electric charge with strength $\epsilon$e, where 
$\epsilon$ is in the range of $10^{-3} -10^{-5}$. [REFERENCE]. This range of parameters makes 
\Aprime{} searches viable in moderate energy fixed target 
electroproduction~\cite{Bjorken:2009mm}, but require large data sets and good mass resolution
to identify a small mass peak above the copious QED background at very small production 
angles. At small couplings, \Aprime's become long-lived, so detection of a displaced decay 
vertex can reject the prompt QED background and boost experimental sensitivity.  These production 
and kinematics poses stringent constraint on the detector requirements:
\begin{itemize}
\item large and uniform acceptance in the forward region close to the beam in order to catch boosted 
\Aprime{} decay products,
\item beam passage through the apparatus in vacuum, to eliminate direct interactions with the 
detector and minimize beam gas interactions, 
\item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 
50~kHz,
\item excellent track reconstruction efficiency for electrons and positrons,
\item good angular and momentum resolution to reconstruct invariant mass precisely,
\item excellent vertex resolution to discriminate displaced \Aprime{} decays from prompt QED 
backgrounds,
\item high rate electronics with excellent timing resolution to minimize out of time backgrounds,
\item data handling rates of 100~MB/s to permanent storage,
\item detector components that can survive and efficiently operate in a high radiation environment 
with local doses exceeding $100$~Mrad.
\end{itemize}
The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and 
vertex signatures by placing a $\approx 1$~m long silicon tracking and vertexing detector 10~cm 
downstream  of a 0.25\%~$\chi_0$ tungsten target inside a dipole magnet. The experiment runs at high 
rates (up to 50kHz), exploiting the 
100\% duty cycle of the Thomas Jefferson National Accelerator Facility (JLab) CEBAF accelerator to 
accumulate the need statistics. The trigger is provided by a fast electromagnetic calorimeter just 
downstream of the tracking detector.

The HPS Test apparatus, a simplified version of the full HPS experiment, was proposed and 
approved at Thomas Jefferson National Accelerator Facility (JLab) as the first stage of the HPS 
experiment. Its purposes included demonstrating that the apparatus and data acquisition systems are 
technically feasible and that the trigger rates and occupancies encountered in electron-beam 
running are as simulated. Given dedicated running time with electron beams, the HPS Test Run 
apparatus is capable of searching for heavy photons in unexplored regions of parameter space.    
The HPS Test apparatus was installed on April 19, 2012, and ran parasitically with the HDice 
experiment~\cite{HDice}, using its photon beam, until May 18. The JLab run schedule 
precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and 
valuable dedicated run with the photon beam. Most technologies used in the Test apparatus will 
be used in the HPS detector with some improvements to each of the systems; both from lessons 
learned during running of the Test run but also from less schedule and budget constraints.

This paper reviews the HPS Test Run apparatus; documents the performance of the trigger, 
data acquisition, silicon tracking detector, and the electromagnetic calorimeter at the level assumed 
in calculating the physics reach of the HPS experiment.

@@

\section{Detector Overview}
\label{detector}
{\small
\begin{figure*}[t]
\begin{center}
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{center}
\end{figure*}
}
The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
499~MHz beam, at an energy of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
The overall design of the experiment follows from the kinematics of \Aprime{} production which 
typically results in final state particles within a few degrees of the incoming beam, especially at low 
$m_{\textrm{A}^\prime}$. Detectors must therefore be placed close to the beam. 
The intense electron beam and the degraded electrons after the target are spread out horizontally by 
the analyzing magnet constitute a "dead zone" which must be completely avoided. The apparatus is 
split vertically $15$~mrad above and below the beam plane and the beam is transported in vacuum 
to minimize beam-gas interaction backgrounds. Even so, background occupancy in the detectors 
remain high and are dominated by the degraded primary beam, so high rate detectors, a fast trigger, 
and excellent time tagging are required to minimize their impact.  
At masses below $2 m_\mu$ only decays to electrons are allowed, so the key trigger comes from a PbWO$_{4}$ crystal calorimeter. 
 %\begin{multicols}{2}
\begin{center}
\begin{table*}[t]
{\small
\caption{Overview of the coverage, segmentation and performance of the HPS Test detector. }
\begin{tabular}{lccccccc}
\hline 
System & Coverage & \# channels & ADC & Time resolution & \# layers & Segmentation & Performance \\
 & (mrad) &  & (bit) & (ns) &  &  &  \\
\hline
SVT & $15<\theta_{y} < XXXX$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
& &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
\hline
ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.3\times1.3$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
 &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
\hline
\end{tabular}
\label{tab:detector-overview}
}
\end{table*}
\end{center}
%\end{multicols}
A rendering of the HPS Test apparatus installed on the beam line is shown in 
Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
given in Tab.~\ref{tab:detector-overview}.

@@

\section{The HPS Test Run Beamline}
The HPS Test run studied multiple Coulomb scattering of electrons and positrons from 
bremsstrahlung photons produced in the Hall B tagged photon facility. 
Figure~\ref{fig:hpstest_layout} shows the layout of 
the HPS Test setup on the beam line. The SVT was installed inside the Hall B pair 
spectrometer magnet (PS) vacuum chamber with the ECal mounted downstream of it. Both the 
SVT and the ECal were retracted off the beam plane compared to nominal electron beam runing to 
allow clean passage of the photon beam through the system. 
\begin{figure}[]
    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
\caption{\small{Layout of the HPS parasitic run.} }
\label{fig:hpstest_layout}
\end{figure}

@@

magnet. Data was taken on three different converter thicknesses with a beam current varying between 
30-70~nA and repeated with the reverse field setting of the PS dipole magnet.
\begin{table}[]
\begin{center}
{\small
\begin{tabular}{|c|c|c|}
\hline
Converter thickn. & Duration &  $e^-$ on converter \\
 (\%$X_0$) & (s) & ($\mu$C)    \\   
\hline
%\hline
1.6   & 911 &   24.4 \\ %24385.9     \\ %27 nA
%\hline
0.18   & 2640 &   193.5 \\ % 193508.9  \\  %73 nA
%\hline
0.45  & 2149 &     140.7 \\ %  140709.9  \\ %65.5 nA
%\hline
0    & 1279  &   88.1 \\ %88079.6  \\
\hline
\end{tabular}
}
\caption{Measured integrated currents for the dedicated photon runs.}
\label{tab:currents}
\end{center}
\end{table}
The photon beam line during the test run produced a relatively large fraction of pairs 
originating upstream of the converter position. This contribution was measured during data taking 
with ``empty'' converter runs i.e. removing the converter but with all other conditions the same. 
The runs taken during the dedicated HPS Test run is summarized in Tab.~\ref{tab:currents}.

@@

\subsection{SVT Data Acquisition}
%igitization, Event Building and Data Transmission}
\label{sec:svt_daq}
The SVT DAQ is based on the Reconfigurable Cluster Element (RCE) and cluster 
interconnect concept developed at SLAC as generic building blocks for DAQ systems. 
The RCE is a generic computational building block, housed on a separate daughter card called 
Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board 
(COB), see Fig.~\ref{fig:cob}.
 \begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=6cm]{figures/svt_daq_module}
	\caption{The SVT DAQ COB board with four data processing daughter cards (DPMs) visible on the left side.}
	\label{fig:cob}
}
\end{center}
\end{figure}
The first generation RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
A schematic overview of the system is shown in Fig.~\ref{fig:svtdaq}. 
 \begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=8cm]{figures/svt-daq-sketch}
	\caption{Block diagram overview of the SVT DAQ.}
	\label{fig:svtdaq}
}
\end{center}
\end{figure}
The analog outputs of up to 12 SVT half-modules (60 APV25 ASICs) are digitized on the Rear-Transition-
Module (RTM), a custom board 
on the back side of the ATCA crate, interfacing the HPS readout to the generic DAQ components on the 
COB. A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to 
the sensitive range of a 14-bit ADC operating at the system clock of 41.667~MHz. The RTM is organized 
into four sections with each section supporting three SVT half-module hybrids (15 APV25 ASICs). The 
RTM also includes a 4-channel fiber optic module and supporting logic which is used to interface 
to the JLab trigger system supervisor. Each section of the RTM is input to a DPM which apply thresholds 
for data reduction and organizes the sample data into UDP datagrams. The DPM also hosts an I$^{2}$C 
controller used to configure and monitor the APV25 ASICs. A single ATCA crate with two COB cards 
was used, one supporting four DPMs and one supporting 3 DPMs and one DPM that is configured as 
the trigger and data transmission module. The two COB cards and their DPMs are interconnected with a 
10Gb/s switch card~\cite{Larsen:2011zb} which also hosts two 1Gb/s Ethernet interfaces to the external 
SVT DAQ PC.

@@

\subsection{Multiple Coulomb Scattering Distributions}
One of the main goals of the HPS Test run was to evaluate the description of the tails of the 
multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 
experiment. Those occupancies have been evaluated using \egs{}~\cite{egs5} simulation program 
whose \moliere{} formulation of multiple scattering show good agreement with previous studies 
for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} . 
Despite all data taken with a photon beam in the Test run, the angular distribution of the pair 
produced electron and positron emerging from the converter with different converter thickness can 
be used to study the varying multiple Coulomb scattering contribution (pair production angle is constant). 
Restricting clusters to a well calibrated region of the ECal we observe, within our systematic 
uncertainties , good agreement with the rates predicted by \egs{}, see Tab.~\ref{tab:ang_distr_dataMC}.
%\begin{center}
\begin{table}
{\small
\begin{tabular}{|l|c|c|c|}
\hline
\bf Converter (\%~$X_0$) & \bf 1.60 & \bf 0.45 &	\bf 0.18 \\
\hline
EGS5 &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
\hline
GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
\hline
Observed 	& 1064 $\pm$ 2 & 196 $\pm$ 1 &	92 $\pm$ 1 \\						
\hline
\end{tabular}
\caption{ Observed and predicted number of events for 1~s of beam at 90~nA for three different converter 
thicknesses. The uncertainty on the prediction includes systematic uncertainties from ECal alignment, background normalization, beam current normalization and limited statistics in the simulation.}
}
\label{tab:ang_distr_dataMC}
\end{table}
%\end{center}

>>>>

%% main text
\section{Introduction}
\label{introduction}
Heavy photons, aka "hidden sector" or "dark" photons, or from here on \Aprime{}, are particles with 
mass $10-1000$~MeV 
which couple weakly to the Standard Model photon~\cite{Holdom:1985ag}, so can be radiated by 
electrons, and can decay 
into \ee pairs, albeit at rates far below those of QED trident processes. They have been suggested by 
numerous Beyond Standard Model theories and as an explanation of the current muonic $g-2$ 
anomaly, and may couple directly to hidden sector particles that may constitute all or some of the 
dark matter~\cite{ArkaniHamed:2008qn}. 
Current phenomenology highlights the $20-1000$~MeV/c$^{2}$ mass range, and 
suggests that \Aprime's couple to electric charge with strength $\epsilon$e, where 
$\epsilon$ is in the range of $10^{-3} -10^{-5}$. [REFERENCE]. This range of parameters makes 
\Aprime{} searches viable in moderate energy fixed target 
electroproduction~\cite{Bjorken:2009mm}, but require large data sets and good mass resolution
to identify a small mass peak above the copious QED background at very small production 
angles. At small couplings, \Aprime's become long-lived, so detection of a displaced decay 
vertex can reject the prompt QED background and boost experimental sensitivity.

The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and 
vertex signatures by placing a $\approx 1$~m long silicon tracking and vertexing detector 10~cm 
downstream  of a 0.25\%~$\chi_0$ tungsten target inside a dipole magnet. The experiment runs at high 
rates (up to 50kHz), exploiting the 
100\% duty cycle of the Thomas Jefferson National Accelerator Facility (JLab) CEBAF accelerator to 
accumulate the need statistics. The trigger is provided by a fast electromagnetic calorimeter just 
downstream of the tracking detector.

The HPS Test apparatus, a simplified version of the HPS experiment, was proposed and 
approved at Thomas Jefferson National Accelerator Facility (JLab) as the first stage of HPS. 
Its purposes included demonstrating that the apparatus and data acquisition systems are 
technically feasible and that the trigger rates and occupancies encountered in electron-beam 
running are as simulated. Given dedicated running time with electron beams, the HPS Test Run 
apparatus is capable of searching for heavy photons in unexplored regions of parameter space.    
The stringent constraints on the detector requirements therefore also applied to the Test detector:
\begin{itemize}
\item large and uniform acceptance in the forward region close to the beam in order to catch boosted 
\Aprime{} decay products,
\item beam passage through the apparatus in vacuum, to eliminate direct interactions with the 
detector and minimize beam gas interactions, 
\item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 
50~kHz,
\item excellent track reconstruction efficiency for electrons and positrons,
\item good angular and momentum resolution to reconstruct invariant mass precisely,
\item excellent vertex resolution to discriminate displaced \Aprime{} decays from prompt QED 
backgrounds,
\item high rate electronics with excellent timing resolution to minimize out of time backgrounds,
\item data handling rates of 100~MB/s to permanent storage,
\item detector components that can survive and efficiently operate in a high radiation environment 
with local doses exceeding $100$~Mrad.
\end{itemize}

The Test apparatus was installed on April 19, 2012, and ran parasitically with the HDice 
experiment~\cite{HDice}, using its photon beam, until May 18. The JLab run schedule 
precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and 
valuable dedicated run with the photon beam. Most technologies used in the Test apparatus will 
be used in the HPS detector with some improvements to each of the systems; both from lessons 
learned during running of the Test run but also from less schedule and budget constraints.

This paper reviews the HPS Test apparatus; documents the performance of the trigger, 
data acquisition, silicon tracking detector, and the electromagnetic calorimeter at the level assumed 
in calculating the physics reach of the HPS experiment.

@@

\section{Detector Overview}
\label{detector}
{\small
\begin{figure*}[t]
\begin{center}
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{center}
\end{figure*}
}
The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
499~MHz beam, at an energy of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
The overall design of the experiment follows from the kinematics of \Aprime{} production which 
typically results in final state particles within a few degrees of the incoming beam, especially at low 
$m_{\textrm{A}^\prime}$. Detectors must therefore be placed close to the beam. 
The intense electron beam and the degraded electrons after the target are spread out horizontally by 
the analyzing magnet constitute a "dead zone" which must be completely avoided. The apparatus is 
split vertically $15$~mrad above and below the beam plane and the beam is transported in vacuum 
to minimize beam-gas interaction backgrounds. Even so, background occupancy in the detectors 
remain high and are dominated by the degraded primary beam, so high rate detectors, a fast trigger, 
and excellent time tagging are required to minimize their impact.  
At masses below $2 m_\mu$ only decays to electrons are allowed, so the key trigger comes from a PbWO$_{4}$ crystal calorimeter. 
 %\begin{multicols}{2}
\begin{center}
\begin{table*}[t]
{\small
\caption{Overview of the coverage, segmentation and performance of the HPS Test detector. }
\begin{tabular}{lccccccc}
\hline 
System & Coverage & \# channels & ADC & Time resolution & \# layers & Segmentation & Performance \\
 & (mrad) &  & (bit) & (ns) &  &  &  \\
\hline
SVT & $15<\theta_{y} < XXXX$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
& &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
\hline
ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.3\times1.3$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
 &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
\hline
\end{tabular}
\label{tab:detector-overview}
}
\end{table*}
\end{center}
%\end{multicols}
A rendering of the apparatus installed on the beam line is shown in 
Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
given in Tab.~\ref{tab:detector-overview}.

@@

\section{The HPS Test Run Beamline}
The HPS Test run studied multiple Coulomb scattering of electrons and positrons from 
bremsstrahlung photons produced in the Hall B tagged photon facility. 
Figure~\ref{fig:hpstest_layout} shows the layout of 
the setup on the beam line. The SVT was installed inside the Hall B pair 
spectrometer magnet (PS) vacuum chamber with the ECal mounted downstream of it. Both the 
SVT and the ECal were retracted off the beam plane compared to nominal electron beam runing to 
allow clean passage of the photon beam through the system. 
\begin{figure}[]
    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
\caption{\small{Layout of the HPS parasitic run.} }
\label{fig:hpstest_layout}
\end{figure}

@@

 Data was taken on three different converter thicknesses with a beam current varying between 
30-70~nA and repeated with the reverse field setting of the PS dipole magnet.
\begin{table}[]
\begin{center}
{\small
\begin{tabular}{|c|c|c|}
\hline
Converter thickn. & Duration &  $e^-$ on converter \\
 (\%$X_0$) & (s) & ($\mu$C)    \\   
\hline
%\hline
1.6   & 911 &   24.4 \\ %24385.9     \\ %27 nA
%\hline
0.18   & 2640 &   193.5 \\ % 193508.9  \\  %73 nA
%\hline
0.45  & 2149 &     140.7 \\ %  140709.9  \\ %65.5 nA
%\hline
0    & 1279  &   88.1 \\ %88079.6  \\
\hline
\end{tabular}
}
\caption{Measured integrated currents for the dedicated photon runs.}
\label{tab:currents}
\end{center}
\end{table}
The photon beam line during the test run produced a relatively large fraction of pairs 
originating upstream of the converter position. This contribution was measured during data taking 
with ``empty'' converter runs i.e. removing the converter but with all other conditions the same. 
The runs taken during the time dedicated to HPS Test is summarized in Tab.~\ref{tab:currents}.

@@

\subsection{SVT Data Acquisition}
%igitization, Event Building and Data Transmission}
\label{sec:svt_daq}
The SVT DAQ is based on the Reconfigurable Cluster Element (RCE) and cluster 
interconnect concept developed at SLAC as generic building blocks for DAQ systems. 
The RCE is a generic computational building block, housed on a separate daughter card called 
Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board 
(COB), see Fig.~\ref{fig:cob}.
 \begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=6cm]{figures/svt_daq_module}
	\caption{The SVT DAQ COB board with four data processing daughter cards (DPMs) visible on the left side.}
	\label{fig:cob}
}
\end{center}
\end{figure}
The first generation RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
A schematic overview of the system is shown in Fig.~\ref{fig:svtdaq}. 
 \begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=8cm]{figures/svt-daq-sketch}
	\caption{Block diagram overview of the SVT DAQ.}
	\label{fig:svtdaq}
}
\end{center}
\end{figure}
The analog outputs of up to 12 SVT half-modules (60 APV25 ASICs) are digitized on the Rear-Transition-
Module (RTM), a custom board 
on the back side of the ATCA crate, interfacing the HPS-specific readout to the generic DAQ components 
on the 
COB. A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to 
the sensitive range of a 14-bit ADC operating at the system clock of 41.667~MHz. The RTM is organized 
into four sections with each section supporting three SVT half-module hybrids (15 APV25 ASICs). The 
RTM also includes a 4-channel fiber optic module and supporting logic which is used to interface 
to the JLab trigger system supervisor. Each section of the RTM is input to a DPM which apply thresholds 
for data reduction and organizes the sample data into UDP datagrams. The DPM also hosts an I$^{2}$C 
controller used to configure and monitor the APV25 ASICs. A single ATCA crate with two COB cards 
was used, one supporting four DPMs and one supporting 3 DPMs and one DPM that is configured as 
the trigger and data transmission module. The two COB cards and their DPMs are interconnected with a 
10Gb/s switch card~\cite{Larsen:2011zb} which also hosts two 1Gb/s Ethernet interfaces to the external 
SVT DAQ PC.

@@

\subsection{Multiple Coulomb Scattering Distributions}
One of the main goals of the Test run was to evaluate the description of the tails of the 
multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 
experiment. Those occupancies have been evaluated using \egs{}~\cite{egs5} simulation program 
whose \moliere{} formulation of multiple scattering show good agreement with previous studies 
for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} . 
Despite all data taken with a photon beam in the Test run, the angular distribution of the pair 
produced electron and positron emerging from the converter with different converter thickness can 
be used to study the varying multiple Coulomb scattering contribution (pair production angle is constant). 
Restricting clusters to a well calibrated region of the ECal we observe, within our systematic 
uncertainties , good agreement with the rates predicted by \egs{}, see Tab.~\ref{tab:ang_distr_dataMC}.
%\begin{center}
\begin{table}
{\small
\begin{tabular}{|l|c|c|c|}
\hline
\bf Converter (\%~$X_0$) & \bf 1.60 & \bf 0.45 &	\bf 0.18 \\
\hline
EGS5 &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
\hline
GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
\hline
Observed 	& 1064 $\pm$ 2 & 196 $\pm$ 1 &	92 $\pm$ 1 \\						
\hline
\end{tabular}
\caption{ Observed and predicted number of events for 1~s of beam at 90~nA for three different converter 
thicknesses. The uncertainty on the prediction includes systematic uncertainties from ECal alignment, background normalization, beam current normalization and limited statistics in the simulation.}
}
\label{tab:ang_distr_dataMC}
\end{table}
%\end{center}
